Error-Centric Annotation of Learner Corpora

### 2009-04-09 text/paper.tex
aaaaaaaaaaaaaaaaaaaaaaaaaaaaaa

Section \ref{sec:scheme} will introduce the general idea behind our annotation
scheme and elaborate on more technical details. Section 3  gives a brief
overview of real world performance of our method, as far as this is indeed
possible. An annotation manual is contained in Appendix A.

@@

@@

The context mechanism in our annotation scheme can increase the complexity of the annotation
process drastically. Since our annotation technique requires us to build a
non-hierarchical graph structure over our input\footnotemark, a traditional
sequential markup scheme scheme that operates directly on the text or spans
over a piece of text will run into at least two kinds of problems:

\footnotetext{Relating words and their dependencies more like a net than as a
hierarchically nested span over a character sequence}

Based on these assumptions, we decided to decouple the \textit{error markup}
from the \textit{corpus data}. Specifically, to our annotation method, the
errors and the text are two entirely different data structures. Every particular
error can reference tokens within the corpus using a \textbf{key}, similar to
the way modern Relational Data Bases reference their data. This makes the index
more accessible and easier to maintain and eliminates both problems above,
because every single annotation can be completely independent from all other
annotations.  The source files for our corpus consisted of plain text files from
the NOCE-corpus of beginning to intermediate Spanish learners of English. Our
corpus format is defined in \ref{def:errorformat}.

@@

\subsection{Limitations}
Word order errors still pose a particular complication even to a non-sequential
scheme such as ours. We are not able to account for the complex dependencies
occurring in some word order mistakes simply by a dependency-graph.

Since our minimal atomic unit is a token, we depend on a tokenization process.
Furthermore, we cannot account for mistakes that occur on a scale smaller than a
token.

>>>>

Section \ref{sec:scheme} will introduce the general idea behind our annotation
scheme and elaborate on more technical details. Section 4 gives a brief overview
of real world performance of our method. An annotation manual is contained in
Appendix A.

@@

Firstly, every annotation scheme that operates directly on the text or spans
over a piece of text will run into two kinds of problems:

Based on these assumptions, we decided to decouple the \textit{error markup}
from the \textit{corpus data}. Specifically, to our annotation method, the
errors and the text are two entirely different data structures. Every
particular error can reference tokens within the corpus using a \textbf{key},
similar to the way modern Relational Data Bases reference their data. This makes
the index more accessible and easier to maintain and eliminates both problems
above, because every single annotation can be completely independent from all
other annotations.

@@

The source files for our corpus consisted of plain text files from the
NOCE-corpus (\cite{negrilloph})
of beginning to intermediate Spanish learners of English. Our corpus
format is defined in \ref{def:errorformat}

@@

\subsection{Limitations}
Some elements, for example word order errors have enforced context, but it is hard to express via our schema, so we don't do it. 
No correct positions specified by word order errors - also hard to express. One could assign them a target position after an existing token, but then one must also keep track of other "reorderings" by multiple word order errors - I would like beer some to drink - here, both erroneous units - some and to drink should be placed between like and beer, but one must take care to order them correctly. Also, as our schema tags all possible errors, in the case of interchangeable errors (cf XXX), one cannot be certain if the error annotated is really the one, made by the learner, and not the other possible one. Most  importantly, there are sometimes more than one places where a word sequence can fit in.

Errors within a token cannot be analyzed – for example, agglutination, because a token is our smallest unit.
